Weighted vs Unweighted

### 2025-02-08 Rmd/weighted_vs_unweighted_proportions.Rmd
run some updated scenarios

y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y7_ebs_pcod_Brett.RDS")

@@

Use
```{r}
ggplot(data=df, aes(x=bin, y=freq, colour=type)) + 
  geom_line() +
  geom_area(aes(fill=type, group=type), alpha = 0.5, position = "identity")

>>>>

# y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y2_ebs_pcod_Brett.RDS")
# y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/y7_ebs_pcod_Brett.RDS")
y2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y2_ebs_pcod_Brett.RDS")
y7 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/inputs/y7_ebs_pcod_Brett.RDS")

@@

Use
```{r}
df.temp = df
df.temp$type[df.temp$type=="Nom"] = "Nominal"
df.temp$type[df.temp$type=="Exp"] = "Expanded"
df.temp %>% 
  tidytable::rename("Composition" = type) -> df.temp

ggplot(data=df.temp, aes(x=bin, y=freq, colour=Composition)) + 
  geom_line() +
  geom_area(aes(fill=Composition, group=Composition), alpha = 0.5, position = "identity") +
  scale_x_continuous(limits = c(20, 110)) +
  labs(x = "Length (cm)", y = "Frequency")
